A thesis draft

### 2018-11-24 res/sections/07-Introduction.tex
Fix typos

Through the history of Internet, many factors changed and new innovations came,
but at the end of the day a fundamental key remains: connection performances
are, indeed, what the users really want.
Today, connectivity plays an important role in everyone's life. Several decades 
brought solutions with enhanced wired and wireless connectivity, like 
Ethernet, Fast Ethernet, 2G, 3G, LTE, and better communication protocols such 
as a whole plethora of TCP standards in order to keep up with the continuous 
surging of network traffic. Internet Service Providers to be able to 
efficiently process the whole quantity of packets passing through the network, 
applies several optimizations along the packet path. Until this day, these 
optimizations have mostly been based on costly, in hardware solutions. In 
particular, these Network Functions are able to perform only generic packet 
elaboration, since they do not know the Quality of Service required by every 
connection. It is in this context that 5G proposes a new way to approach 
networking, suggesting the virtualization of this Network Functions, making 
their deployments faster and cheaper. On top of that, it proposes specific 
services for determined kind of data. If in the past a train running a 
300km/h had to use the same network services of an IoT device sending data 
updates every hour, now 5G proposes two different and efficient solutions for 
this completely different services. This separation is performed through the 
creation of determined network components called Network Slices. This new 
possibility of offering the network with specialized class of services, 
combined with emerging virtualization technologies like cloud computing, 
hypervisor-virtualized machine or container-based solutions enables the 
deployment of Virtualized Network Functions within seconds running on generic 
purpose or custom hardware. While there may be some performances degreadations, 
it has been demonstrated that their time-to-deploy and the possibility of 
automation they offers are unprecedented~\cite{nguyen2017sdn}. On top of 
that, specialized software acts as a MANager and Orchestrator (MANO) for this 
VNFs, regulating their lifecycle. While most of the current proposals are based 
on hypervisor on cloud solutions, in this thesis we are going to see a 
proof-of-concept of a part of a Network Slice, equipped with a custom MANO 
solution, based on the new container-based technology, called Docker, on a 
recent orchestrator framework: Kubernetes.

>>>>

Through the history of Internet, many factors changed and new innovations came,
but at the end of the day a fundamental key remains: connection performances
are, indeed, what the users really want. Today, connectivity plays an important
role in everyone's life. Several decades brought solutions with enhanced wired
and wireless connectivity, like Ethernet, Fast Ethernet, 2G, 3G, LTE, and better
communication protocols such as a whole plethora of TCP standards in order to
keep up with the continuous surging of network traffic. Internet Service
Providers to be able to efficiently process the whole quantity of packets
passing through the network, applies several optimization along the packet path.
Until this day, these optimization have mostly been based on costly, in hardware
solutions. In particular, these Network Functions are able to perform only
generic packet elaboration, since they do not know the Quality of Service
required by every connection. It is in this context that 5G proposes a new way
to approach networking, suggesting the virtualization of this Network Functions,
making their deployments faster and cheaper. On top of that, it proposes
specific services for determined kind of data. If in the past a train running a
300km/h had to use the same network services of an IoT device sending data
updates every hour, now 5G proposes two different and efficient solutions for
this completely different services. This separation is performed through the
creation of determined network components called Network Slices. This new
possibility of offering the network with specialized class of services, combined
with emerging virtualization technologies like cloud computing,
hypervisor-virtualized machine or container-based solutions enables the
deployment of Virtualized Network Functions within seconds running on generic
purpose or custom hardware. While there may be some performances degreadation,
it has been demonstrated that their time-to-deploy and the possibility of
automation they offers are unprecedented~\cite{nguyen2017sdn}. On top of that,
specialized software acts as a MANager and Orchestrator (MANO) for this VNFs,
regulating their lifecycle. While most of the current proposals are based on
hypervisor on cloud solutions, in this thesis we are going to see a
proof-of-concept of a part of a Network Slice, equipped with a custom MANO
solution, based on the new container-based technology, called Docker, on a
recent orchestrator framework: Kubernetes.
